An Open Repository of Real-Time COVID-19 Indicators

### 2021-10-06 indicators/paper/paper.tex
Don't depend on prelim.tex
PNAS's system wants to rebuild the LaTeX from scratch, so make it easy.
Include survey consent and IRB information
Requested as part of the PNAS quality check.

\input{../../common/prelim.tex}

@@

\paragraph{Internet-Based Surveys} Conducted in partnership with Facebook,
Delphi's COVID-19 Trends and Impact Survey receives an average of 50,000 responses
daily, and has received over 20 million responses since April 2020
\cite{Salomon:2021, Kreuter:2020}. From the surveys, we construct indicators on
symptoms, social distancing, vaccination, and other attitudes and behaviors
related to COVID.

@@

Altogether, we produce over 170 signals from 12 distinct sources, and provide
them in a common format for public access. This unifies both unique (unavailable
anywhere else) and standard COVID data streams into a single common 
format, enabling efficient comparison and modeling. A summary of the data
sources and signals in the API is in Table~\ref{tab:sources_signals}, and
detailed documentation is available online at
\url{https://cmu-delphi.github.io/delphi-epidata/api/covidcast_signals.html}.

@@

Also notable is the fact that the correlations fluctuate over time in complex
ways; while some of this variation is likely due to changes in public behavior,
reporting and testing practices, and so on, some is also related to changes in
overall COVID-19 case trends. For example, comparing against
Figure~\ref{fig:time_trends_national}, we see that correlations drop in February
2021 for many of the signals, roughly matching the point in time when COVID
cases also sharply decline. This decline likely caused the heterogeneity in case
rates by county to decline, making it more difficult for any signal to achieve a
high geo-wise correlation.

@@

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/backfill-compare.pdf}
  \caption{The 95th percentiles of relative changes between early reported
    values of key signals and final values reported much later. For each date
    between October 15, 2020 and April 15, 2021, the values for each state
    reported between 10 and 90 days later are compared to ``final'' versions
    recorded as of August 13, 2021. Even officially reported case and death data
    can have large revisions 30--60 days or more after initial reporting; much
    of this is driven by individual large revisions affecting specific states
    and dates, rather than systematic changes affecting all states and dates.} 
  \label{fig:backfill-compare}
\end{figure}

Figure~\ref{fig:backfill-compare} shows relative differences between early
indicator values, reported 10--90 days after the underlying events, and later
versions at least four months later. As the distribution of these revision
amounts is highly skewed, the figure plots the 95th percentile of relative
change, showing that reported deaths can incur large relative error in initial
values, comparable to that in claims-based signals.  However, for deaths, as
well as cases, the revision pattern is not very systematic, with large
corrections typically occuring at a sparse subset of locations and times (e.g.,
due to audits or backlogs being cleared, which can result in thousands of cases
or deaths can be added or removed all at once).  This backfill is much more
difficult to predict than that of claims data, therefore the latter (and other
sources) may be useful for nowcasting cases and deaths while public health
reports are being aggregated and corrected.

>>>>

\usepackage{microtype}
\usepackage{booktabs}
\def\cor{\mathrm{cor}}

@@

\paragraph{Internet-Based Surveys} Conducted in partnership with Facebook,
Delphi's COVID-19 Trends and Impact Survey receives an average of 50,000
responses daily, and has received over 25 million responses since April 2020
\cite{Salomon:2021, Kreuter:2020}. From the surveys, we construct indicators on
symptoms, social distancing, vaccination, and other attitudes and behaviors
related to COVID. The surveys are voluntary and participants are redirected to a
platform managed by Carnegie Mellon University to give consent and take the
survey; individual response data is not provided to Facebook and the data
collection protocol was approved by the Carnegie Mellon Institutional Review
Board (STUDY2020\_00000162).

@@

Altogether, we produce over 170 signals from 12 distinct sources, and provide
them in a common format foc access. This unifies both unique (unavailable
anywhere else) and standard COVID data streams into a single common 
format, enabling efficient comparison and modeling. A summary of the data
sources and signals in the API is in Table~\ref{tab:sources_signals}, and
detailed documentation is available online at
\url{https://cmu-delphi.github.io/delphi-epidata/api/covidcast_signals.html}.

@@

Also notable is the fact that the correlations fluctuate over time in complex
ways; while some of this variation is likely due to changes in public behavior,
reporting and testing practices, and so on, some is also related to changes in
overall COVID-19 case trends. For example, comparing against
Figure~\ref{fig:time_trends_national}, we see that correlations drop in February
2021 for many of the signals, roughly matching the point in time when COVID
cases also sharply decline. This decline likely caused the heterogeneity in case
rates by county to decline, making it more difficult for any signal to achieve a
high geo-wise correlation. Correlations between confirmed cases and cases 1--3
weeks prior (shown in the Supplementary Information) show a similar correlation
drop in February 2021, showing that the drop is due to a change in case data and
not problems with the other signals.

@@

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{backfill-compare.pdf}
  \caption{The 95th percentiles of relative error of early reported values of
    key signals compared to final values reported much later. For each date
    between October 15, 2020 and April 15, 2021, the values for each state
    reported between 10 and 90 days later are compared to ``final'' versions
    recorded as of August 13, 2021. Even officially reported case and death data
    can have large revisions 30--60 days or more after initial reporting; much
    of this is driven by individual large revisions affecting specific states
    and dates, rather than systematic changes affecting all states and dates.}
  \label{fig:backfill-compare}
\end{figure}

Figure~\ref{fig:backfill-compare} shows relative differences between early
indicator values, reported 10--90 days after the underlying events, and later
versions at least four months later. As the distribution of these revision
amounts is highly skewed, the figure plots the 95th percentile of relative
change, showing that reported deaths can incur large relative error in initial
values, comparable to that in claims-based signals. However, for deaths, as well
as cases, these large revisions are not very systematic, with large corrections
typically occurring at a sparse subset of locations and times (e.g., due to 
audits or backlogs being cleared, which can result in thousands of cases or
deaths can be added or removed all at once). This backfill is much more
difficult to predict than that of claims data, therefore the latter (and other
sources) may be useful for nowcasting cases and deaths while public health
reports are being aggregated and corrected.
